### 2012-10-02 doc/prelim/document/chapters/introduction/introduction.tex
fixed typo in intro

The computational resources required to solve such problems are
tremendous. Recent work in modeling coupled fluid flow and solid
material heat and mass transfer in a reactor subsystem, similar to the
same components of the departure from nucleate boiling example above,
was performed as part of analysis of the Department of Energy's
Consortium for Advanced Simulation of Light Water Reactors (CASL)
modeling and simulation hub using the Drekar multiphysics code
developed at Sandia National Laboratories
\citep{pawlowski_drekar_2012}. Using Drekar, multiphysics simulations
have been performed with fully consistent methods for the solution of
nonlinear systems using meshes of $O(\sn{1}{9})$ elements leveraging
$O(100,000)$ cores on leadership class machines. Neutronics components
to be implemented in CASL for multiphysics analysis, such as the
Denovo radiation transport code developed at Oak Ridge National
Laboratory \citep{evans_denovo:_2010}, computes trillions of unknowns
for full core reactor analysis on $O(\sn{1}{9})$ element meshes and
$O(100,000)$ cores as well. Given the large scale and complexity of
these problems, if we aim to advance multiphysics solution techniques,
then we are motivated to advance the solution of complex and general
nonlinear problems exploiting leadership class levels of parallelism.

>>>>

The computational resources required to solve such problems are
tremendous. Recent work in modeling coupled fluid flow and solid
material heat and mass transfer in a reactor subsystem, similar to the
same components of the departure from nucleate boiling example above,
was performed as part of analysis of the Department of Energy's
Consortium for Advanced Simulation of Light Water Reactors (CASL)
modeling and simulation hub using the Drekar multiphysics code
developed at Sandia National Laboratories
\citep{pawlowski_drekar_2012}. Using Drekar, multiphysics simulations
have been performed with fully consistent methods for the solution of
nonlinear systems using meshes of $O(\sn{1}{9})$ elements leveraging
$O(100,000)$ cores on leadership class machines. Neutronics components
to be implemented in CASL for multiphysics analysis, such as the
Denovo radiation transport code developed at Oak Ridge National
Laboratory \citep{evans_denovo:_2010}, compute trillions of unknowns
for full core reactor analysis on $O(\sn{1}{9})$ element meshes and
$O(100,000)$ cores as well. Given the large scale and complexity of
these problems, if we aim to advance multiphysics solution techniques,
then we are motivated to advance the solution of complex and general
nonlinear problems exploiting leadership class levels of parallelism.
